A continental-scale analysis finds generalists, with large clutch size and residual brain mass, are the most urban-tolerant of birds

### 2018-05-29 ms.Rmd
some more phylo justification

### Phylogenetic analysis
For the phylogenetic portion of our analyses, we used the phylogenetic trees provided by Jetz et al. [@jetz2012global]. This phylogeny represents the first completely mapped phylogeny of 9,993 birds [@jetz2012global]. In order to assess whether there was a phylogenetic signal [@revell2008phylogenetic; @munkemuller2012measure] of the urbanization index and the continuous predictor variables used in our study, we used the phylosignal package [@keck2016phylosignal] in the R computing environment [@r2017coreteam]. This was also conducted for each of the continuous response variables in order to assess the relative contribution of phylogeny on the predictor variables.

Phylogenetic models were fit based on the same global model as above, but using the 'phylolm' function from the phylolm package which fits a linear regression model where the likelihood is linear in the number of tips in the tree [@ho2014phylolm]. Similar to above, we model-averaged the global phylogenetic model using the aforementioned methods.  We also  fit the same model to a range of the equally likely trees from [@jetz2012global] examining the distribution of putatively important parameters across the distribution of trees.

>>>>

### Phylogenetic analysis
As the correlation between traits and urbanization may be influenced by the shared evolutionary history of the species [felsenstein1985phylogenies], we also a used phylogenetically informed model to test the hypothesis. Phylogenetically informed models are descendents of phylogenetic indepedent contrasts [felsenstein1985phylogenies], which in simple terms, tests for repeated evolutionary association between the traits of interest.  Or in this particular case, whether the traits of interest (e.g. large brain size at a given body size) repeatedly allow for the use of urban areas wherever it evolved across the bird phylogeny.  We used the phylogenetic trees provided by Jetz et al. [@jetz2012global]. This phylogeny represents the first completely mapped phylogeny of 9,993 birds [@jetz2012global]. In order to assess whether there was a phylogenetic signal [@revell2008phylogenetic; @munkemuller2012measure] of the urbanization index and the continuous predictor variables used in our study, we used the phylosignal package [@keck2016phylosignal] in the R computing environment [@r2017coreteam]. This was also conducted for each of the continuous response variables in order to assess the relative contribution of phylogeny on the predictor variables.

Phylogenetic models were fit based on the same global model as above, but using the 'phylolm' function from the phylolm package which fits a linear regression model where the likelihood is linear in the number of tips in the tree [@ho2014phylolm]. Similar to above, we model-averaged the global phylogenetic model using the aforementioned methods.  To account for aspects of phylogenetic uncertainty, we also fit the same model to a range of the equally likely trees from [@jetz2012global] examining the distribution of putatively important parameters across the distribution of trees.
